---
title: "Road Traffic Accidents in the UK"
author: "InterstellR"
date: "March 27, 2018"
output: github_document
---

```{r load-packages, message=FALSE, warning=FALSE, echo=FALSE}
library(tidyverse)
```

```{r load-data, message=FALSE, echo=FALSE}
accidents <- read_csv("../data/uk-traffic-accidents.csv")
```

## Section 1. Introduction

Due to the increasing amounts of traffic accidents in recent years, which were cause to an estimated 40,000 deaths in 2016 in the United States alone ([source](http://fortune.com/2017/02/15/traffic-deadliest-year/)), for our research project, we want improve our understanding of the causes of such accidents. Specifically, we will try to answer what factors impact the likelihood and severity of road accidents. We will do so by looking at car accident data for the city of Leeds in West Yorkshire, England, from the year 2014. The dataset was published by the Leeds City Council and can be found [here](https://data.gov.uk/dataset/road-traffic-accidents/resource/fa7bb4b9-e4e5-41fd-a1c8-49103b35a60f). Unfortunately, the publisher does not provide the methodology by which the data was collected. The dataset contains 2533 rows, each of which represents a single accident for a single person. If multiple people were involved in an accident, they appear as separate entries. In total, there are 16 variables, which are described in detail in the accompanying codebook. These reveal information such as the time, place, severity, and weather conditions of the accident as well as the gender and age of the person involved. We hope that a this analysis will allow us to uncover the major causes of accidents and aid as a source for improvements to traffic safety and accident prevention.

## Section 2. Data analysis plan

## Section 3. Data
